Stack Safety as a Security Property

### 2020-07-08 main.tex
Definition 6.6

\definition{Top-level stack testing property}
%
  \ldots wrap the coinductive stack testing property

>>>>

\definition
%
  A trace $\MPT$ satisfies our \emph{top-level stack testing property} if it
  satisfies the eager testing property at depth 1 with regard to the initial
  variant, $\mathit{stack}_T ~ 1 ~ \MPT ~ \vm{\contour_0}$.
%
  \rb{I don't think the initial variant has been defined, but it's
    straightforward.}
